Constant-sized correlations are sufficient to robustly self-test maximally entangled states with unbounded dimension

### 2019-09-14 Draft/ext_abstract.tex
QIP version

% AMS
\usepackage{amsmath,amssymb,amsfonts,amsthm,amstext}
\usepackage{bbm}

@@

\renewcommand{\Re}{\operatorname{Re}}
\renewcommand{\Im}{\operatorname{Im}}
\DeclareMathOperator{\vc}{vec}
\DeclareMathOperator{\spn}{span}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\spec}{spec}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\hook}{hook}
\DeclareMathOperator*{\E}{\mathbb{E}}
\DeclareMathOperator{\supp}{supp}

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\EXT}{EXT}
\newcommand{\LS}{LS}
\newcommand{\COMM}{COMM}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\tO}{\tilde{O}}
\newcommand{\tP}{\tilde{P}}
\newcommand{\tQ}{\tilde{Q}}
\newcommand{\tM}{\tilde{M}}
\newcommand{\tN}{\tilde{N}}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}
\newcommand{\ux}{\underline{x}}
\newcommand{\uc}{\underline{c}}
\newcommand{\ua}{\underline{a}}
\newcommand{\ub}{\underline{b}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\ba}{\pmb{a}}
\newcommand{\bb}{\pmb{b}}
\newcommand{\bc}{\pmb{c}}
\newcommand{\bS}{\mathbbmtt{S}}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{claim}[theorem]{Claim}
\newtheorem*{conjecture*}{Conjecture}
\newtheorem*{problem}{Problem}
\newtheorem*{example}{Example}

@@

%%%%%%%%%%%%%%%%
%   Document   %
%%%%%%%%%%%%%%%%

\begin{document}

@@

\author[1]{Honghao Fu}

\renewcommand\Affilfont{\itshape\small}

\affil[1]{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA}
%\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
\maketitle

\begin{abstract}
	We show that for any prime odd integer $d$, there exists a correlation of size $\Theta(r)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$,
	where $r$ is the smallest multiplicative generator of $\Zd$.
	The construction of the correlation uses the embedding procedure
	proposed by Slofstra (\textit{Forum of Mathematics, Pi.} Vol.~$7$ Cambridge University Press, $2019$).
	Since there are 
	infinitely many prime numbers whose smallest multiplicative generator
	is at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimensions.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
The certification of a quantum device is an important building block
for many quantum information processing tasks, especially
when the devices are provided by some untrusted vendor.
We would like such certification to be done based solely on
the observed measurement statistics and with the only assumption that
any local device cannot communicate their own
inputs to the other local devices. 
The measurement statistics are referred to as correlations.

It has been shown that certain quantum correlations require the distant parties to share
a particular entangled state up to some local isometry. 
This phenomenon is referred to as self-testing.  
If we can further prove that, when the observed correlation deviates 
from the ideal one to some extent, 
the shared state is close to the ideal state up to some local isometry,
then we say the self-test is robust.

Self-testing is powerful because only classical interactions are performed.
Hence, it allows a classical party to delegate quantum computations to some untrusted service provider
and verify that the computations are performed
honestly and correctly \cite{ruv2013,coladan2017verifier}.
It also becomes a critical component of the security proofs of device-independent quantum cryptographic protocols
\cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.
Since the setting of interactive proof systems is similar to a self-test, self-testing arguments also help to prove
lower bounds of the computational power of entanglement-assisted
multiprover interactive proof systems \cite{fitzsimons2019, neexp}.

The case of robust self-testing of the EPR pair, 
\begin{align*}
    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
\end{align*}
is fully understood.
The techniques for this case are 
first introduced in \cite{mckague2012}, then improved in \cite{bamps2015}. 
Robust self-testing of partially entangled qubits is proved later in
\cite{yang2013}, which also proposed an generalized swap-isometry
that can be used to robustly self-test large dimensional maximally entangled states.
Robust self-testings of tensor product of maximally and partially entangled qubits 
are proved in \cite{coladan2016parallel,natarajan2017,lowdegree},
with the last one being the one with the smallest input and output alphabets.
Self-testing of all pure bipartite entangled states is proved in \cite{coladan2017all}.
The authors in \cite{coladan2017all} constructed a family of correlations such
that an entangled state of any local dimension has
a self-testing correlation in this family.
% One can also self-test many copies of the $2$-dimensional EPR
% pair in parallel \cite{mckague2016,natarajan2017,coladan2016parallel}.
% The most efficient way uses $O(\log n)$ bits question and
% answers to self-test $n$ copies of $2$-dimensional EPR
% pair \cite{lowdegree}.
% Self-testing general $d$-dimensional EPR pairs is a harder task.
% Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
To generate a correlation in the family, Alice and Bob
use constant-sized input alphabets but $\Theta(d)$-sized output alphabets, 
where $d$ is the local dimension of the entangled state. 
This is the only result about self-testing the general $d$-dimensional entangled state so far.
However, proving the robustness of this family of correlations remains an open problem.

Our work aims at answering two open questions.
The first one is whether maximally entangled states with large local dimension
can be self-tested with constant-sized input and output alphabets, 
which are independent of the local dimension of the self-tested state.
For comparisons, all the correlations used in the results listed above
have either input or output alphabets with sizes dependent on the
local dimension of the entangled state.
The second one is how to robustly self-test maximally entangled states
with large local dimension and no tensor product structure. 
We give an affirmative answers to the first question and
make significant progress in answering the second question
by proving the following theorem.
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}
The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.

The set $D$ is, specifically, the set of all 
odd prime numbers whose smallest primitive root 
is either $2$, $3$, or $5$, 
We say that $r$ is a primitive root of $d$ if $r$ is the 
multiplicative generator of the group $\Zd$.
It has been shown that $D$ has infinitely many elements \cite{murty1988}.

To prove \cref{thm:inf}, we construct a correlation with $\Theta(r)$-sized
input and constant-sized output alphabets
for each odd prime number $d$ whose smallest primitive root is $r$.
This correlation is denoted by $\fC(d,r)$.
Note that although the size of the input or output alphabet of $\fC(d,r)$ does not depend on $d$, 
the distributions in $\fC(d,r)$ do. 
Once we prove $\fC(d,r)$ can robustly self-test a maximally entangled
state of dimension $4(d-1)$, we apply it to all $d \in D$
and prove \cref{thm:inf}.
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}

The correlation $\fC(d,r)$ contains a winning correlation of a specially-designed binary linear system game.
In a general linear system game, Alice is given a random equation 
from a linear system and she
should give an assignment to each variable of the equation.
Bob is asked to assign a value to a random variable of that equation.
They win the game if Alice's assignment satisfies the equation and Bob's
assignment to the variable matches Alice's assignment.
A widely-used and thoroughly-studied example of a linear system game is
the Magic Square game \cite{magic_square}.
In this game, the linear system is
\begin{align*}
    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
    x_7 + x_8 + x_9 = 0 \\
    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
    x_3 + x_6 + x_9 = 0.
\end{align*}
Using two copies of $\ket{EPR}$
the Magic square game can be won with certainty.
It has been shown that if a strategy that can win this game almost perfectly, 
the shared state must be close to $\ket{EPR}^{\x 2}$ up to some local isometry \cite{wu2016}, 
so we can say that the Magic Square game can robustly self-test $\ket{EPR}^{\x 2}$.
The key observation that leads to the self-testing proof is that 
a winning strategy must contain binary observables $X$ and $Z$ that 
satisfy the anti-commutation relation 
\begin{align*}
    X Z = - Z X.
\end{align*}
Intuitively, we can think of the Magic Square game as a way to enforce the
anti-commutation relation \cite{coladan2017}.

Our linear system game is designed to enforce the relation 
\begin{align*}
    U O U\ct = O^r,
\end{align*}
for unitaries $U$ and $O$, and some integer $r$.
It implies that the winning strategy contains binary observables
$M_1, M_2, M_3, M_4$ on Alice's side and 
$N_1, N_2, N_3, N_4$ on Bob's side such that 
\begin{align*}
    U = M_3M_4 = N_3N_4 && O = M_1M_2 = N_1N_2.
\end{align*}
This relation implies the eigenvalues of $O$ must be $\omega_d^j = e^{ij2\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root is $r$. 
It also implies that $U$ is a permutation of the eigenbasis of $O$.
Winning this linear system game implies that Alice and Bob share a state
$\ket{\psi}$ such that
\begin{align*}
    O \x O \ket{\psi} = \ket{\psi}, && 
    U \x U \ket{\psi} = \ket{\psi}.
\end{align*}
These two relations are important for the self-testing argument.
The relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
is spanned by tensor products of states in the eigenbasis of $O$.
The relation $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
under the permutation induced by $U$. 
At this point, the eigenvalues of $O$ are unknown, so
certifying the eigenvalues of $O$ requires another test, 
which will be introduced later.

The special feature of our linear system game is that the sizes
of the question sets for Alice and Bob are of order $\Theta(r)$,
and the answer sets are of size $\Theta(1)$.
Restricting $r \leq 5$ as in \cref{thm:inf} implies that our linear system 
game only uses constant-sized question sets and constant-sized answer sets.

@@

The remaining question is how to certify eigenvalues of $O$, so we
design a nonlocal test called the extended weighted CHSH test.
% Before going to the answer,
% we remark that 
% the other specialty of the linear system game is that it forces Alice and Bob to have binary observables
% whose products are the special unitaries $U$ and $O$, because the answers to the questions of the 
% linear system games are binary. 
% The idea of decompose the unitaries of arbitrary order into binary observables was also first introduced by Slofstra \cite{slofstra2017}.
% We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, 
% The fact that Alice and Bob only have binary observables make it easier for us 
% to compose the linear system game with another nonlocal test, which we call the extended weighted CHSH test.
The difference between a nonlocal game and a nonlocal test will be discussed later.
The combination of a linear system game with 
a nonlocal test in the construction of $\fC(d,r)$ 
is a new way to use a linear system game for robust self-testing.
It distinguishes our approach from all the previous ones.

The extended weighted CHSH test is designed based on the $\alpha$-weighted CHSH inequality, 
\begin{align*}
    \I_\alpha = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
\end{align*}
where $M_x$ and $N_y$ for $x,y \in \{1, 2\}$ are some binary observables.
Define $\mu = \arctan(1/\alpha)$,
\begin{align*}
    \pauliz = \ketbra{0}{0} - \ketbra{1}{1} && \paulix = \ketbra{0}{1} + \ketbra{1}{0},
\end{align*}
which are the Pauli-Z and Pauli-X operators.
This inequality is maximally violated when the shared state is $\ket{EPR}$,
Alice's binary observables are
\begin{align*}
    \tM_1 = \pauliz && \tM_2 = \paulix,
\end{align*}
and Bob's binary observables are
\begin{align*}
    \tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix  && \tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix。
\end{align*}
We first prove that the maximal violation of $\I_\alpha$ can robustly self-test the shared
state $\ket{\psi}$ and the observables $\tM_1, \tM_2$ and $\tN_1, \tN_2$ in \cref{sec:ext_chsh}.
Then we notice that 
\begin{align*}
    \tN_1\tN_2 = \cos(2\mu) \1  - \sin(2 \mu) \pauliz \paulix 
\end{align*}
has eigenvalues $e^{i 2\mu}$ and $e^{-i 2\mu}$.

Therefore, in the extended weighted CHSH test, we set $\alpha = \cot( -\pi/d )$
for some odd prime $d$ whose primitive root is $r$,
and ask Alice and Bob
to reuse the observables $M_1, M_2$ and $N_1, N_2$ defined in $\LS(r)$. Then we can certify that
the unitary $O = M_1M_2 = N_1N_2$ has eigenvalues $e^{i2\pi/d}$ and $e^{-i2\pi/d}$.
Combining this observation with the fact that $O$ satisfy the relation $UOU\ct = O^r$,
we can conclude that all the eigenvalues of $O$ are $\{ e^{ij 2\pi /d} \}_{j=1}^{d-1}$,
and the eigenspaces of all the eigenvalues have the same cardinality.

At this point, we have the explicit structure of $O$, so we 
can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
to prove the correlation $\fC(r, d)$ can robustly self-test 
a maximally entangled state of dimension $4(d-1)$,
\begin{align*}
    \left(\frac{1}{\sqrt{d}} \sum_{j=1}^{d-1}\ket{j}\ket{d-j}\right)\x 
    \ket{EPR}^{\x 2}.
\end{align*}

In the proof, we demonstrate a new way to apply the generalized swap-isometry
proposed in \cite{yang2013} to robustly self-test a maximally entangled state of large local
dimension. This is the first application of the generalized swap-isometry in the robust self-testing proof.

Our contributions are:
\begin{enumerate}
\item We identify a family of correlations with constant-sized input and output alphabets that can be used to robustly self-test
maximally entangled states with unbounded local dimensions. Before our work, the most efficient way 
was to use $O(\log d)$-sized input and $O(\log \log d)$-sized output alphabets to robustly self-test
the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.

\item Our result gives us deeper understandings of the set of quantum correlations.
In previous works that proved the non-closeness of the set of quantum correlations \cite{slofstra2017, slofstra2018}, 
lower bounds of the entanglement required to achieve certain correlations are identified.
We discover a large family of correlations such that we know exactly the entangled state
required to achieve each of the correlations in this family. 
\end{enumerate}

\textbf{Structure of the paper}.
We start with notations and background information in \cref{sec:prelim}.
Since the correlation we designed can win a special linear system game and satisfy
an extended weighted CHSH test, we introduce the linear system game
in \cref{sec:lsg} and the extended weighted CHSH test in \cref{sec:ext_chsh}. 
Then we give the correlation $\fC(d,r)$ and the ideal strategy to generate it in \cref{sec:full_test}.
In the end, we give the robust self-testing proof in \cref{sec:main}.

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
%-----------------------------------
\subsection{Notations and mathematical background}
%-----------------------------------
The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we self-test is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
\end{align}
The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$.

In the qubit case, the EPR pair is denoted by 
\begin{align}
	\ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
\end{align}
and the Pauli operators are denoted by
\begin{align}
	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
\end{align}
Note that we only work with finite Hilbert spaces in our work.

>>>>

% AMS
\usepackage{amsmath,amssymb,amsfonts,amsthm,amstext}

@@

\renewcommand{\Re}{\operatorname{Re}}
\renewcommand{\Im}{\operatorname{Im}}
\DeclareMathOperator{\vc}{vec}
\DeclareMathOperator{\spn}{span}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\spec}{spec}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\hook}{hook}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\supp}{supp}

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\EXT}{EXT}
\newcommand{\LS}{LS}
\newcommand{\COMM}{COMM}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\tP}{\tilde{P}}
\newcommand{\tQ}{\tilde{Q}}
\newcommand{\tM}{\tilde{M}}
\newcommand{\tN}{\tilde{N}}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}
\newcommand{\ux}{\underline{x}}
\newcommand{\uc}{\underline{c}}
\newcommand{\ua}{\underline{a}}
\newcommand{\ub}{\underline{b}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\ba}{\pmb{a}}
\newcommand{\bb}{\pmb{b}}
\newcommand{\bc}{\pmb{c}}
\newcommand{\bS}{\mathrm{S}}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{claim}[theorem]{Claim}
\newtheorem*{conjecture*}{Conjecture}
\newtheorem*{problem}{Problem}
\newtheorem*{example}{Example}

@@

%%%%%%%%%%%%%%%%
%   Document   %
%%%%%%%%%%%%%%%%
\vspace{-8ex}
\date{}
\begin{document}

@@

\author{Honghao Fu}

\maketitle

The certification of a quantum device is an important building block
for many quantum information processing tasks, especially
when the devices are provided by some untrusted vendor.
We would like such certification to be done based solely on
the observed measurement statistics with the only assumption being that
any local device cannot communicate their own
inputs to the other local devices. 
The measurement statistics are referred to as correlations.

It has been shown that certain quantum correlations require the distant parties to share
a particular entangled state up to some local isometry. 
This phenomenon is referred to as self-testing.  
If we can further prove that, when the observed correlation deviates from 
the ideal correlation to some extent, 
the shared state is close to the ideal state up to some local isometry,
then we say the self-test is robust.

Self-testing is powerful because only classical interactions are performed.
Hence, it allows a classical party to delegate quantum computation tasks to some untrusted service provider
and verify that the computations are performed
honestly and correctly \cite{ruv2013,coladan2017verifier}.
It also becomes a critical component of the security proofs of device-independent quantum cryptographic protocols
\cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.
Since the setting of interactive proof systems is similar to a self-test, self-testing arguments also help to prove
lower bounds of the computational power of entanglement-assisted
multiprover interactive proof systems \cite{fitzsimons2019, neexp}.

Robust self-testing of the EPR pair, 
$\ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11})$,
is first proved in \cite{mckague2012}, then 
the techniques are improved in \cite{bamps2015}.
Robust self-testing of partially entangled qubits is later proved in
\cite{yang2013}.
Robust self-testing results of tensor product of maximally and partially entangled qubits 
are proved in \cite{coladan2016parallel,natarajan2017,lowdegree},
with the last one being the one with the smallest input and output alphabet.
For general bipartite entangled quantum states, \cite{coladan2017all} proves that there exists a family of correlations such that
each bipartite entangled state can be self-tested by a correlation in this family.
% The authors constructed a family of correlations such
% that each partially or maximally entangled state of any local dimension has
% a self-testing correlation in this family.
% One can also self-test many copies of the $2$-dimensional EPR
% pair in parallel \cite{mckague2016,natarajan2017,coladan2016parallel}.
% The most efficient way uses $O(\log n)$ bits question and
% answers to self-test $n$ copies of $2$-dimensional EPR
% pair \cite{lowdegree}.
% Self-testing general $d$-dimensional EPR pairs is a harder task.
% Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}

There are two open questions about self-testing that we aim at answering.
The first one is whether maximally entangled states with large local dimension
can be self-tested with constant-sized input and output alphabets. 
For comparisons,
all the self-testing correlations used in the results listed above have 
output alphabets with size depending on $d$
when they try to self-test an entangled state of local dimension $d$.
The second one is how to robustly self-test maximally entangled states
with local dimension $d > 2$ and $d \neq 2^n$ for any $n$.
For example, the authors of \cite{coladan2017all} left proving their
family of self-testing correlations robust as an open problem.

We give an affirmative answer to the first question
and make significant progress in answering the 
second question
by proving the following theorem.  
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
	with constant-sized input and output alphabets.
\end{theorem}
Formal statements of this theorem can be found in Theorem $6.16$ and $6.17$
of the attached report.
% The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.

\textbf{Sketch of the proof}.
The set $D$ is, specifically, the set of all 
odd prime numbers whose smallest primitive root 
is either $2$, $3$, or $5$, 
We say that $r$ is a primitive root of $d$ if $r$ is a 
multiplicative generator of the group $\Zd$.
It has been shown that $D$ has infinitely many elements \cite{murty1988}.

To prove \cref{thm:inf}, we construct a correlation with $\Theta(r)$-sized
input and constant-sized output alphabets
for each $d \in D$ whose smallest primitive root is $r$.
This correlation is denoted by $\fC(d,r)$.
Note that although the size of the input or output alphabet of $\fC(d,r)$ does not depend on $d$, 
the distributions in $\fC(d,r)$ do. 
Details of $\fC(d,r)$ can be found in Section $5$ of the attached report.
% Then we prove the robust self-testing property of $\fC(d,r)$ by showing 
% that if some quantum strategy can approximate $\fC(d,r)$, then
% the generalized swap isometry \cite{yang2013},
% \hf{which only involves local operations,} 
% can produce a state that is close to the desired maximally entangled state, when applied to the unknown state used in the strategy.  
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}

The correlation $\fC(d,r)$ contains a winning correlation of a specially-designed binary linear system game.  
In a general binary linear system game, Alice is asked for an assignment of a random equation 
of a linear system.
Bob is asked to assign a value to a random variable of that equation.
The assignment to each variable is binary. 
They win the game if Alice's assignment satisfies the equation and Bob's
assignment to the variable matches Alice's assignment.
Intuitively, binary linear system games are designed to enforce certain
relations between observables possessed by Alice and Bob.
For example. the Magic Square game \cite{magic_square} forces
Alice and Bob to have binary observables $X$ and $Z$ such that $XZ = -ZX$ \cite{wu2016, coladan2017}.

In his seminal work \cite{slofstra2017}, Slofstra proved that 
there exists a binary linear system game that cannot be won by any finite-dimensional quantum strategy but a limit of 
finite-dimensional strategy can win it perfectly,
which implies that the set of quantum correlations generated by
finite-dimensional strategies is not closed.
In the proof, he proposed and validated a new way 
to design binary linear system games to enforce conjugacy relations of the
form $X Y X\ct = Z$ for unitaries $X, Y$ and $Z$.
Following Slofstra's work, we design our binary linear system game, $\LS(r)$,
to enforce the relation $U O U\ct = O^r$ for some unitaries $U$ and $O$.
By enforcing this relation we mean that, 
if some quantum strategy with shared state $\ket{\psi}$
wins this game with probability $1 - \ep$,
then one can identify unitaries $U_A, O_A$ on Alice's side and
$U_B, O_B$ on Bob's side as products of their binary observables, such that 
\begin{align}
\label{eq:induct}
	 U_A O_A U_A\ct \ket{\psi} \appd{O(r \se)}  O_A^{r} \ket{\psi}.
\end{align}
The analogous relation holds on Bob's side too.
The construction of $\LS(r)$ is given in Section $3$ and
the proof of \cref{eq:induct} is given in Section $6.1$ of the attached report.

The special feature of our linear system game is that the sizes
of the input alphabets for Alice and Bob are of order $\Theta(r)$,
and the output alphabets are of size $\Theta(1)$.
Restricting $r \leq 5$ as in \cref{thm:inf} implies that our linear system 
game only uses constant-sized input and output alphabets.

@@

\Cref{eq:induct} is not sufficient for self-testing, so
$\fC(d,r)$ also contains an extension of the optimal correlation 
that achieves the maximal violation of the $\cot(-\frac{\pi}{d})$-weighted CHSH inequaltiy \cite{pal2010}
\begin{align*}
    \I_{\cot(-\pi/d)} = \cot(-\frac{\pi}{d})(\ip{M_1N_1} + \ip{M_1N_2}) + \ip{M_2N_1} - \ip{M_2N_2}.
\end{align*}
In Section $4$, we prove that $\I_{\cot(-\pi/d)}$ can be used to robustly
self-test $\ket{EPR}$ and rotated Pauli operators.
% The extended correlation has input alphabets $\{0,1,2, \nr+1, \nr+2\}$ for Alice and Bob, where $\nr$ is the number of variables of
% the linear system game introduced above,
% and output alphabets with size $3$.
% If some strategy with shared state $\ket{\psi}$ can produce a correlation that is within
% expected trace distance $\ep$ from this correlation, 
% we first identify a special sub-normalized state $\ket{\psi_1} = 1/2(M_{\nr+1}^0 + iM_{\nr+2}M_{\nr+1}^1 - iM_{\nr+2}M_{\nr+1}^0 +M_{\nr+1}^1) \ket{\psi}$, such that
% \begin{align*}
%     &O_A \ket{\psi_1} \appd{O(\sd \qe)} \omega_d^{-1} \ket{\psi_1}, \\
%     &O_B \ket{\psi_1} \appd{O( \qe/\sd)} \omega_d\ket{\psi_1}.
% \end{align*}
By investigating this extended correlation, we find a sub-normalized state
$\ket{\psi_1}$ such that,
if some strategy with shared state $\ket{\psi}$ can produce a correlation that is within
expected trace distance $\ep$ from $\fC(d,r)$, then
\begin{align}
    \label{eq:decomp}
    \ket{\psi} \appd{O( r^{d/2} \ep^{1/8})}
    \sum_{j=1}^{(d-1)} (U_A\ct U_B\ct)^{\log_r j} \ket{\psi_1},
\end{align}
where $\log_r j $ is the discrete log.
This decomposition of $\ket{\psi}$ is the key observation that enables the application of the generalized swap-isometry.  
\Cref{eq:decomp} is 
proved in Section $6.2$ of the attached report, which uses \cref{eq:induct}.

The combination of a linear system game with 
additional correlations in the construction of $\fC(d,r)$ 
is a new way to use linear system games for robust self-testing.
It distinguishes our approach from all the previous ones.

Our robust self-testing proof applies two
local isometries $\Phi_{A,1} \x \Phi_{B,1}$ and
$\Phi_{A,2} \x \Phi_{B,2}$ sequentially to the state $\ket{\psi}$, where $\Phi_{A,1} \x \Phi_{B,1}$ is 
illustrated in the figure below and 
$\Phi_{A,2} \x \Phi_{B,2}$ is the standard qubit swap-isometry used 
in the robust self-testing proof of the Magic Square game \cite{wu2016}.
\begin{figure}[H]
\center
        \begin{tikzpicture}[thick]
        %
        % `operator' will only be used by Hadamard (H) gates here.
        % `phase' is used for controlled phase gates (dots).
        % `surround' is used for the background box.
        \tikzstyle{operator} = [draw,fill=white,minimum size=1.5em] 
        \tikzstyle{phase} = [fill,shape=circle,minimum size=5pt,inner sep=0pt]
        \tikzstyle{surround} = [fill=blue!10,thick,draw=black,rounded corners=2mm]
        %
        % Bracket
        \draw[decorate,decoration={brace,mirror},thick] (0,-1) to
    	node[midway,left] (bracket1) {$\ket{\psi}$}
    	(0,-2);
        % Qubits
        \node at (0,0) (q1) {$\ket{0}$};
        \node at (0,-1) (q2) {};
        \node at (0,-2) (q3) {};
        \node at (0,-3) (q4) {$\ket{0}$};
        %
        % Column 1
        \node[operator] (op11) at (1,0) {$QFT_d$} edge [-] (q1);
        \node[operator] (op14) at (1,-3) {$QFT_d$} edge [-] (q4);
        %
        % Column 3
        \node[phase] (phase11) at (2,0) {} edge [-] (op11);
	\node[operator] (op22) at (2,-1) {$O_A$} edge [-] (q2);
	\node[operator] (op23) at (2, -2) {$O_B$} edge[-] (q3);
        \node[phase] (phase14) at (2,-3) {} edge [-] (op14);
        \draw[-] (phase11) -- (op22);
        \draw[-] (phase14) -- (op23);
        %
        % Column 4
        \node[operator] (op31) at (3,0) {$QFT_d^{-1}$} edge [-] (phase11);
        \node[operator] (op34) at (3,-3) {$QFT_d^{-1}$} edge [-] (phase14);
        %
        % Column 5
        \node[phase] (phase21) at (4,0) {} edge [-] (op31);
	\node[operator] (op42) at (4,-1) {$U_A$} edge [-] (op22);
	\node[operator] (op43) at (4, -2) {$U_B$} edge[-] (op23);
        \node[phase] (phase24) at (4,-3) {} edge [-] (op34);
        \draw[-] (phase21) -- (op42);
        \draw[-] (phase24) -- (op43);
        %
        % Column 6
        \node (end2) at (5,-1) {} edge [-] (op42);
        \node (end3) at (5,-2) {} edge [-] (op43);
        %
        % Bracket
        \draw[decorate,decoration={brace},thick] (5,-1) to
    	node[midway,right] (bracket) {$\ket{\psi_1}$}
    	(5,-2);
        %
        % Column 7
        \node (end1) at (6.5,-0.5) {} edge [-] (phase21);
        \node (end4) at (6.5,-2.5) {} edge [-] (phase24);
        % Dashed line
        \draw[loosely dotted] (0,-1.5) -- (5,-1.5);
        % Bracket
        \draw[decorate,decoration={brace},thick,] (6.5,-0.5) to
    	node[midway,right] (bracket2) {$\sum_{j=1}^{d-1}\ket{j}\ket{d-j}$}
    	(6.5,-2.5);
        %
        % Background Box
        \begin{pgfonlayer}{background} 
        \node[surround] (background) [fit = (q1) (op14) (bracket1)(bracket2)] {};
        \end{pgfonlayer}
        %
        \end{tikzpicture}
	\caption{The isometries $\Phi_{A,1} \x \Phi_{B,1}$.}
\end{figure}
Note that $QFT_d$ denotes the generalized Quantum Fourier Transform.
With the help of \cref{eq:decomp}, we can prove that
\begin{align*}
    \Phi_{A,1}\x\Phi_{B,1}(\ket{\psi}) \appd{O(d r^{d} \ep^{1/8})} \sqrt{d-1}\ket{\psi_1} \x \frac{1}{\sqrt{d-1}}\sum_{j=1}^{d-1} \ket{j}\ket{d-j}.
\end{align*}
This is the first application of the generalized swap-isometry \cite{yang2013} to a robust self-testing proof.  
Applying the second isometry to the state $\sqrt{d-1}\ket{\psi_1}$ gives us that
\begin{align*}
    \Phi_{A,2}\x\Phi_{B,2}(\sqrt{d-1}\ket{\psi})
    \appd{O(\sr \se)} \ket{junk} \x 
    \ket{EPR}^{\x 2}.
\end{align*}
Details about these two isometries can be found in
Section $6.4$ of the attached report.
